### 2016-07-21 R/ITHIM.Rmd

```{r loadITHIM, message = FALSE, eval = TRUE, warning = FALSE, error = TRUE}
library("devtools")
install("~/ITHIM/")
#install_github("syounkin/ITHIM")
library("ITHIM")
```

>>>>

```{r loadITHIM, message = FALSE, eval = TRUE, warning = FALSE, error = TRUE}
library("devtools")
#install_github("syounkin/ITHIM", ref="devel")
install("~/ITHIM/")
library("ITHIM")
```
